Bayesian integration of networks without gold standards

### 2011-08-24 src/main/latex/paper/paper.tex
results split up by PPI and GI
Short addition to results

@@

\note{TODO: Show some stats on the integration of real data}

@@

>>>>

\subsection{Evaluation on simulated data}

@@

@@

\subsection{Application to physical and genetic interactions}

Figure \ref{ppi+gi} shows histograms of the existence probabilities for physical and genetic interactions from the semantically integrated dataset as calculated by the method presented here. It is apparent that \note{NUMBER}\% of the experimentally reported protein-protein interactions have been assigned probabilites less than 0.1. This is consistent with the reports of \note{PAPER}.

\begin{figure}[!tpb]
\centerline{\includegraphics[width=.5\textwidth]{fig2.pdf}}
\caption{Histogram of existence probabilities for the interactions in the integrated dataset. Top: Protein-protein interactions, bottom: genetic interactions.}
\label{ppi+gi}
\end{figure}
